### 2022-11-09 NSF2022/Description/backgroundv2.tex

The key idea is to define the dynamics using the following
boundary value problem system:
\begin{alignat}{4}
  -\mu\Delta \uu + \nabla p &= \mathbf{0}, 
  && \nabla \cdot \uu = 0, && \quad \xx \in \Omega(t), \label {eqn:stokes} \\
  \label{eqn:phase}
  -\epsilon^2 \Delta \phi + W'(\phi) &= 0, && &&\quad \xx \in \Omega(t),\\
\label{eqn:noslip}        
\uu(\xx) &= \frac{dF_i}{dt}(\XX,t)
&&=\vv_i + \omega_i \times (\xx - \aa_i), 
&&\quad \xx \in \Gamma_i(t),\\
\label{eqn:material}
\phi(\xx) &= h_i(\XX), &&  &&\quad \xx \in \Gamma_i(t),
\end{alignat}
for $i=1,\ldots,N_b$
and where $\xx = F_i(\XX,t)$.
Finally,
\begin{equation}
\label{eqn:stressbalance}
\int_{\Gamma_i} \left(\sigma  + T_i\right)\nnu \,\dif s = \mathbf{0},\quad
\int_{\Gamma_i} (\xx - \aa_i)\times \left(\sigma + T_i\right) \nnu \,\dif s = \mathbf{0}
\end{equation}
where
\begin{equation}
\label{eqn:hydro_stress}
\sigma = \mu(\nabla \uu + \nabla \uu^T) - pI,\quad 
T_i = -\epsilon^{-1} W'(\phi)I
  + \epsilon\left(\tfrac{1}{2}|\nabla \phi|^2I - \nabla \phi \nabla
  \phi^T\right)
\end{equation}
are the hydrodynamic and phase stresses, respectively; 
$I$ is the $n\times n$ identity matrix.
For vectors $\aa, \bb \in \mathbb{R}^2$,
we follow the usual convention of defining
the ``cross product'' as
$\aa \times \bb = (\aa^{\perp} \cdot \bb) \kk$
where $\kk = (0,0,1) \in \mathbb{R}^3$ and $(a_1,a_2)^{\perp} = (-a_2,a_1)$.

The above form a semi-linear elliptic 
system for evolution of the granules.  Equations~\eqref{eqn:stokes} are the
Stokes equations that describes the velocity $\uu$ and pressure $p$ of
the viscous aqueous phase.  Equation~\eqref{eqn:phase} describes the
phase transitions of the scalar order parameter $\phi$ with a decay
length $\epsilon$.
The scalar function $W(\phi)$ is a well potential where the local 
minimima representing low energy states of the water phase.
Mathematically, this order parameter is responsible for
the attraction and adhesion between granules that want to align boundaries
of like phase.

The next three equations are the moving domain boundary conditions.
Equations~\eqref{eqn:noslip} specify a no-slip
boundary condition for a rigid body with translation velocity $\aa'_i(t) = \vv_i$
and angular velocity $\omega_i$
about the point $\aa_i(t) \in U_i(t)$.
($\omega_i$ is the axial vector of the
skew symmetric matrix $R'_i(t)$.)
In
equation~\eqref{eqn:material}, the function $h_i$ is a material label
specifying the phases at water-granule interface.
The boundary condition for $\phi$ is transported by the flow
and satisfies $\phi_t + \uu \cdot \nabla \phi = 0$ on $\Gamma_i$.
Finally,
equation~\eqref{eqn:stressbalance} closes the system by
requiring that the force and torque generated by 
hydrodynamic stress balances that generated by phase stress $T_i$ in
\eqref{eqn:hydro_stress}.

@@

The system~\eqref{eq:RBT}--\eqref{eqn:stressbalance}
has the energy law
\begin{equation}
\label{eq:energy_law}
  \frac{d}{dt}E
  = - \int_{\Omega_t}\tfrac{1}{2}\mu|\nabla \uu + \nabla
  \uu^T|^2 \,d\xx,\quad
    E = \int_{\Omega(t)}
  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
\end{equation}
Here $E$ is the energy stored in the phase transitions.
Because $E$ depends both on $\phi$ and $\Omega(t)$,
the derivation of \eqref{eq:energy_law}
is somewhat subtle and has been worked out in detail in \cite{Fu2018_SIAM}.
It goes as follows.
Using the Rayleigh Transport Theorem, 
the time derivative out $E$ yields an energy
density flux involving the phase stress $T_i$
at the boundary, plus a bulk term involving 
the Euler-Lagrange derivative of $E.$
The Euler-Lagrange derivative vanishes due to~\eqref{eqn:phase}
and the boundary flux transforms into viscous dissipation due to 
\eqref{eqn:hydro_stress} and the Stokes equations.

Mathematically, a change in granule configuration
instantaneously changes the phase energy $E$
the dynamics are such that energy is lost due to hydrodynamic dissipation.
Further details and generalizations are provided in
the Specific Aim 1 section \ref{sec:specific_aim1}.

>>>>

The key idea is to define the dynamics using the following
boundary value problem system:
\begin{alignat}{4}
  -\mu\Delta \uu + \nabla p &= \mathbf{0}, 
  &&\quad \nabla \cdot \uu = 0, && \quad \xx \in \Omega(t), \label {eqn:stokes} \\
  \label{eqn:phase}
  -\epsilon^2 \Delta \phi + W'(\phi) &= 0, && &&\quad \xx \in \Omega(t),\\
\label{eqn:noslip}        
\frac{dF_i}{dt}(\XX,t) & = \uu(\xx) 
&&=\vv_i + \omega_i \times (\xx - \aa_i), 
&&\quad \xx \in \Gamma_i(t),\\
\label{eqn:material}
\phi(\xx) &= h_i(\XX), &&  &&\quad \xx \in \Gamma_i(t),
\end{alignat}
for $i=1,\ldots,N_b$
and where $\xx = F_i(\XX,t)$.
Finally,
\begin{equation}
\label{eqn:stressbalance}
\int_{\Gamma_i} \left(\sigma  + T_i\right)\nnu \,\dif s = \mathbf{0},\quad
\int_{\Gamma_i} (\xx - \aa_i)\times \left(\sigma + T_i\right) \nnu \,\dif s = \mathbf{0}
\end{equation}
where
\begin{equation}
\label{eqn:hydro_stress}
\sigma = \mu(\nabla \uu + \nabla \uu^T) - pI,\quad 
T_i = \gamma\left[\epsilon^{-1} W'(\phi)I
  + \epsilon\left(\tfrac{1}{2}|\nabla \phi|^2I - \nabla \phi \nabla
  \phi^T\right)\right]
\end{equation}
are the hydrodynamic and phase stresses, respectively; 
$I$ is the $n\times n$ identity matrix.
For vectors $\aa, \bb \in \mathbb{R}^2$,
we follow the usual convention of defining
the ``cross product'' as
$\aa \times \bb = (\aa^{\perp} \cdot \bb) \kk$
where $\kk = (0,0,1) \in \mathbb{R}^3$ and $(a_1,a_2)^{\perp} = (-a_2,a_1)$.

The above form a semi-linear elliptic 
system for evolution of the granules.  Equations~\eqref{eqn:stokes} are the
Stokes equations that describes the velocity $\uu$ and pressure $p$ of
the aqueous region with viscosity $\mu$.  Equation~\eqref{eqn:phase} describes the
phase transitions of the scalar order parameter $\phi$ with a decay
length $\epsilon$.
The scalar function $W(\phi)$ is a well potential where the local 
minimima representing low energy states of the water phase.
Mathematically, this order parameter is responsible for
the attraction and adhesion between granules that want to align boundaries
of like phase.

The next three equations are the moving domain boundary conditions.
Equations~\eqref{eqn:noslip} specify a no-slip
boundary condition for a rigid body with translation velocity $\aa'_i(t) = \vv_i$
and angular velocity $\omega_i$
about the point $\aa_i(t) \in U_i(t)$.
($\omega_i$ is the axial vector of the
skew symmetric matrix $R'_i(t)$.)
In
equation~\eqref{eqn:material}, the function $h_i$ is a material label
specifying the phases at water-granule interface.
The boundary condition for $\phi$ is transported by the flow
and satisfies $\phi_t + \uu \cdot \nabla \phi = 0$ on $\Gamma_i$.
Finally,
equation~\eqref{eqn:stressbalance} closes the system by
requiring that the force and torque generated by 
hydrodynamic stress balances that generated by phase stress $T_i$ in
\eqref{eqn:hydro_stress}.
The parameter $\gamma > 0$ is surface tension.

@@

The system~\eqref{eq:RBT}--\eqref{eqn:stressbalance}
has the energy law
\begin{equation}
\label{eq:energy_law}
  \frac{d}{dt}E
  = - \int_{\Omega_t}\tfrac{1}{2}\mu|\nabla \uu + \nabla
  \uu^T|^2 \,d\xx,\quad
    E = \gamma \int_{\Omega(t)}
  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
\end{equation}
Here $E$ is the energy stored in the phase transitions.
Mathematically, the energy law states that changes
in granule configuration instantaneously change the phase energy $E$.
The dynamics are such that the change energy
is lost due to hydrodynamic dissipation.
Further details and generalizations are provided in
the Specific Aim 1 section \ref{sec:specific_aim1}.

Because $E$ depends both on $\phi$ and $\Omega(t)$,
the derivation of \eqref{eq:energy_law}
is somewhat subtle and has been worked out in detail in \cite{Fu2018_SIAM}.
It goes as follows.
Using the Rayleigh Transport Theorem, 
the time derivative out $E$ yields an energy
density flux involving the phase stress $T_i$
at the boundary, plus a bulk term involving 
the Euler-Lagrange derivative of $E.$
The Euler-Lagrange derivative vanishes due to~\eqref{eqn:phase}
and the boundary flux transforms into viscous dissipation due to 
\eqref{eqn:hydro_stress} and the Stokes equations.

In terms of physical justification, the
derivation of the one-dimensional version of our model
was carried out by \cite{MaRa76} and \cite{ErLjCl89}
using a Landau expansion of the
free energy density for a single-well potential.
The double-well potential case was derived by
Gompper in \cite{GoHaKo94} to describe metastable coordination of water.
In the field of surface chemistry \cite{Israelachvili1954},
there is a large empirical literature on properties of
long-range hydrophobic interaction~\cite{LeRaPa77,KoNa15,
Nagle17,Lum1999, Lin2005, Meyer2006, Ducker2016,Jackson2016,Gletal88,Aketal17,Ch05}.
The stress~\eqref{eqn:stressbalance} was first
identified by PIs Ryham and Young in~\cite{Fu2018_SIAM}
and generalizes one-dimensional hydrophobic interaction to
the $n$-dimensional setting.

Finally, we mention that in the single-well case
$W(\phi) = \tfrac{1}{2}u^2,$ \eqref{eqn:phase} takes the form
of a screened Laplace (SL) equation $-\epsilon^2 \Delta \phi + \phi =0$.
If the material label $h_i = 1$ everywhere, then $\phi$
has a boundary layer going from $1$ at the boundary to $0$ in the bulk
and one can prove that 
\begin{equation}
\label{eqn:math_motivation}
\lim_{\epsilon \to 0} E = \frac{\gamma}{2} \int_{\partial \Omega} 1 \,dS
\end{equation}
under the assumption that $\Omega$ has a class $\mathbf{C}^2$ boundary \cite{}.
In other words, the phase energy can be viewed as an
approximation of surface energy that ``extends'' into the bulk.
In the general case, $h_i^2$ replaces $1$ in \eqref{eqn:math_motivation}.
We are confident that \eqref{eq:RBT}--\eqref{eqn:stressbalance}
is a correct description of long-range surface interactions.
